A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Compact table to fit page
Comment on terminology
Acknowledgements

\small

@@

e{1-12}

@@

@@

\subsection*{Grant information}
% subsection in Schnitte-Anno
% im Großen und Ganzen: Ich habe keine Ahnung, wer meine Ernährer sind
Christian O. Häusler was supported by a graduate stipend from the German federal state of Saxony-Anhalt and ???
Michale Hanke was supported by ???

>>>>

\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}

@@

%e{1-12}

@@

\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the
events that were selected/available to build GLM regressors from them. Hence the term
'event' should be used here, and cross-reference to figure \ref{fig:reg} should be made}
\todo[inline]{what does e1-12 stand for? It makes the label column too wide}

@@

\subsection*{Grant information}

COH was supported by a graduate stipend from the German federal state of
Saxony-Anhalt and MH was supported by funds from the German federal state of
Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
management technology for this study was in part supported by the European
Union’s Horizon 2020 Research and Innovation Programme under Grant Agreement
no. 785907 (HBP SGA2).
